---
title: "R Notebook"
output: html_notebook
---


## Load data from Hufford_etal_2012
```{r}
library(data.table)
library(tidyr)
#AGPv2:GRMZM2G039867, chr3:150,049,274..150,052,250
d <- fread("largedata/Hufford2012/757736/Hufford_et_al._2012_10kb_statistics.txt", data.table=FALSE)

```

## Parameters for MS

### 1. i need 1) genome-wide theta per bp from teosinte, from windows with >50% of the bp sequenced. 
### 2. i need 2) the estimate of rho per bp from those same windows in teosinte.
```{r, eval=FALSE}
library(data.table)
library(tidyr)
#AGPv2:GRMZM2G039867, chr3:150,049,274..150,052,250
d <- fread("largedata/Hufford2012/757736/Hufford_et_al._2012_10kb_statistics.txt", data.table=FALSE)

sub <- subset(d, seqbp >= 5000)
theta_teo <- sub[, c("seqbp", "ThetaWteo", "ThetaPiteo", "ThetaHteo", "S_rhoteo", "rho_teo")]
write.table(theta_teo, "largedata/teo_theta.csv", sep=",", row.names=FALSE, quote=FALSE)

```

### 3. i need 3) sample size in maize and teosinte. 
maize = 35
teosinte = 17

### 4. and i need the length of the window you care about 
(how many bp were sequenced in the window with the gene of interest)

The gene spans two windows, one seqbp = 5494, the other seqbp = 1823.


